Malacology: A Programmable Storage System

### 2016-10-21 paper/paper.tex
paper: prune backoff evaluation
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

We control the conditions for migration using \texttt{when()}. \texttt{when()}
is part the Mantle API and the callback expects a return value of true or
false, which corresponds to whether to migrate or not. For the Mantle curve in
Figure~\ref{fig:mantle-balancer-behaviors} we set the \texttt{when()} policy to
wait for load on the receiving server to fall below a threshold. At the
beginning of the run the load of the receiving server spikes because requests
for cache-coherence start as the sequencers are created. It takes 60 seconds
for this load to drop to an acceptable level and it is at this point that the
migration starts.  The Mantle curve in
Figure~\ref{fig:mantle-balancer-behaviors} also takes longer to reach peak
throughput.  This conservative decision making is intentional because we want
the policy wait to see how migrations affect the system before proceeding. The
Mantle curve in Figure~\ref{fig:mantle-balancer-behaviors} does a migration
right before 50 seconds, realizes that there is a third underloaded server, and
does another migration.

The other way to change aggressiveness of the decision making is to program
into the balancer a threshold for sustatined overload. This forces the balancer
to wait a certain number of iterations after a migration before proceeding. In
Mantle, the policy would use the save state function to do a countdown after a
migation.  Behavior graphs and performance numbers for this backoff feature is
omitted for space considerations, but the throughput graphs are as expected:
the more conservative the approach the less overall throughput.\\

>>>>

We control the conditions for when to migrate using \texttt{when()}, a callback
in the Mantle API.  For the Mantle curve in
Figure~\ref{fig:mantle-balancer-behaviors} we program \texttt{when()} to wait
for load on the receiving server to fall below a threshold. This makes the
balancer more conservative because it takes 60 seconds for cache coherence
messages to settle.  The Mantle curve in
Figure~\ref{fig:mantle-balancer-behaviors} also takes longer to reach peak
throughput because we want the policy to wait to see how migrations affect the
system before proceeding; the balancer does a migration right before 50
seconds, realizes that there is a third underloaded server, and does another
migration.

The other way to change aggressiveness of the decision making is to program
into the balancer a threshold for sustatined overload. This forces the balancer
to wait a certain number of iterations after a migration before proceeding. In
Mantle, the policy would use the save state function to do a countdown after a
migation.  Behavior graphs and performance numbers for this backoff feature is
omitted for space considerations, but our experiments confirm that the more
conservative the approach the less overall throughput.\\
